---
title: "Happy Birthday Abi!"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    toc: no
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(leaflet)
library(dplyr)
library(readr)
library(fontawesome)
library(googlesheets4)
```


You are 24 today!

Now I know you want to know what the plan os for your birthday weekend, so I have made this little page to explain it all! And you can refer to it throughout the weekend!

Now lets get cracking - this video will explain everything:


<video width='100%' controls>   <source src="intro_bday_vid.mp4" type="video/mp4"> </video>


Thats right we will be going on a 2 day food crawl of London! Where we be going I hear you ask? Well, you can browse the overview map and the daily itineraries below :)

# Overview 

```{r load data, include=FALSE}

#data <- read_csv("food_tour_data.csv")

#Read google sheets data into R
data <- read_sheet("https://docs.google.com/spreadsheets/d/1SYMhCFlWBndnX83yumbMijqn4B9Ur9gFtsVYO-KrNFg/edit?usp=sharing")
```


```{r add content, include=FALSE}
data <- data %>% 
  mutate(content =  paste(sep = "",
                          "<b><a href='", url, "'>", 
                          name, "</a></b>",
                          "<br/>",
                          location, 
                          "<br/>",
                          notes,
                          "<br/>",
                          "<img src = ",
                          image,
                          " width= 100>"
                          
  ))
```


```{r create icons, include=FALSE}
icoLst <- awesomeIconList(
    dessert = makeAwesomeIcon(text = fa("ice-cream")),
    italian = makeAwesomeIcon(text = fa("pizza-slice")),
    coffee = makeAwesomeIcon(text = fa("mug-hot")),
    alcohol = makeAwesomeIcon(text = fa("martini-glass-citrus")),
    chinese = makeAwesomeIcon(text = fa("bowl-rice")),
    bakery = makeAwesomeIcon(text = fa("cookie-bite")),
    main = makeAwesomeIcon(text = fa("drumstick-bite")),
    sandwich = makeAwesomeIcon(text = fa("burger"))
  )

```

# Map

```{r map, echo = F}

leaflet(data = data) %>% 
  addTiles() %>%
  addAwesomeMarkers(~long, ~lat, 
                    popup = ~content, 
                    label = ~as.character(name),
                    icon = ~icoLst[icon],
                    group = ~icon)
```

